---
title: "Food Security Survey Analysis EDA"
output: html_document
date: "2024-01-05"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
knitr::opts_chunk$set(warning = FALSE, message = FALSE) 

library(tidyverse)
library(haven)
library(janitor)
library(knitr)
library(survey)
# Read in data -------------------------------------------------------------------

df <- read_sav("data/nov/[9800] Amplify AAPI M3 November 2023 - Final Data - 20240109.sav") |> clean_names()

 
# Coding food security status ----------------------------------------------------

# Responses of “often” or “sometimes” on questions HH3 and HH4, and “yes” on AD1, AD2, and AD3 are coded as affirmative (yes). Responses of “almost every month” and “some months but not every month” on AD1a are coded as affirmative (yes). The sum of affirmative responses to the six questions in the module is the household’s raw score on the scale.
df <- df |> mutate(hh3 = case_when(q1a <3 ~ 1),
                   hh4 = case_when(q1b <3 ~ 1),
                   ad1 = case_when(q3 == 1 ~ 1),
                   ad1a = case_when(q4 <3 ~ 1),
                   ad2 = case_when(q5 == 1 ~ 1),
                   ad3 = case_when(q6 == 1 ~ 1)) |>
           rowwise() |>
           mutate(score = sum(c(hh3, hh4, ad1, ad1a, ad2, ad3), na.rm = T))

# Calculate food security status
df <- df |> mutate(
  fs = case_when(score <2 ~ "high",
                 score > 1 ~ "low")
)

# Recode values
df <- df |> mutate(
 age4= case_when(age4 ==1 ~ "18-29",
            age4 ==2 ~ "30-44",
            age4 ==3 ~ "45-59",
            age4 ==4 ~ "60+",
            age4 == 9 ~ "Under 18"
            ),
 asianorigin = case_when(asianorigin ==1 ~ "Chinese",
                         asianorigin ==2 ~ "Asian Indian",
                         asianorigin ==3 ~ "Filipino",
                         asianorigin ==4 ~ "Vietnamese",
                         asianorigin ==5 ~ "Korean",
                         asianorigin ==6 ~ "Japanese",
                         asianorigin ==7 ~ "NHPI",
                         asianorigin ==8 ~ "Other singular AAPI",
                         asianorigin ==9 ~ "Multiple AAPI"
                         
                         )
)


```


## Calculating Food Security Scores According to the FDA

#### Food security status is assigned as follows:

- Raw score 0-1—High or marginal food security (raw score 1 may be considered marginal food security, but a large proportion of households that would be measured as having marginal food security using the household or adult scale will have raw score zero on the six-item scale)

- Raw score 2-4—Low food security

- Raw score 5-6—Very low food security

For some reporting purposes, the food security status of households with raw score 0-1 is described as food secure and the two categories “low food security” and “very low food security” in combination are referred to as food insecure.

```{r food security, echo= FALSE, results='asis',fig.align='left' }
kable(df |> count(score))
```

## Age Breakdown of Food Security 

```{r age, echo=FALSE}
# Age breakdown
age <- df |> group_by(fs, age4) |> 
  summarise(count = n())  |>
  group_by(age4)|>
  mutate(proportional_count = count / sum(count)) |>
  select(-count) |>
  pivot_wider(names_from = age4, values_from = proportional_count, values_fill = 0)

kable(age)

```

## Ethnicity Breakdown of Food Security

``` {r asianorigin, echo = FALSE}
# Asian origin breakdown
ao <- df |> group_by(fs, asianorigin) |> 
  summarise(count = n())|> 
  group_by(asianorigin)|>
  mutate(proportional_count = count / sum(count)) |>
  select(-count) 

kable(ao |>
  pivot_wider(names_from = asianorigin, values_from = proportional_count, values_fill = 0))

ggplot(ao, aes(x=asianorigin, y = proportional_count, fill = fs)) + 
  geom_bar(stat="identity", show.legend=F) + coord_flip() + 
  scale_fill_manual(values = c('#00BFC4', '#F8766D')) + 
  facet_wrap(~fs, scales = "free_y")


svy <- svydesign(ids=~1, weights = ~weight, data = df)


ao_svy <- svyby(~fs, by = ~asianorigin, design = svy, FUN = svytotal) |> as_tibble()

kable(ao_svy)

```

## Age Breakdown for Demographic Group

```{r age and demo, echo = FALSE}
demo_fx <- function(demo) {
  df <- df |> filter(asianorigin == demo) |> group_by(fs, age4) |> 
  summarise(count = n())  |>
  group_by(age4)|>
  mutate(proportional_count = count / sum(count)) |>
  select(-count) |>
  pivot_wider(names_from = age4, values_from = proportional_count, values_fill = 0)
  
  kable(df, caption = demo)
}

lapply(unique(df$asianorigin), demo_fx)

```

## Country of Origin Breakdown
```{r coo, echo = FALSE}
# Country of origin breakdown
coo <- df |> group_by(fs, coo) |> 
  summarise(count = n())|> 
  group_by(coo)|>
  mutate(proportional_count = count / sum(count)) |>
  select(-count) |>
  pivot_wider(names_from = coo, values_from = proportional_count, values_fill = 0)
age 

kable(coo)

```