---
title: "Food Security Survey Analysis EDA"
output: html_document
date: "2024-01-05"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
knitr::opts_chunk$set(warning = FALSE, message = FALSE) 

library(tidyverse)
library(haven)
library(janitor)
library(knitr)
library(survey)
library(scales)
# Read in data -------------------------------------------------------------------

source("002_recode.R")


```


## Calculating Food Security Scores According to the FDA

#### Food security status is assigned as follows:

- Raw score 0-1—High or marginal food security (raw score 1 may be considered marginal food security, but a large proportion of households that would be measured as having marginal food security using the household or adult scale will have raw score zero on the six-item scale)

- Raw score 2-4—Low food security

- Raw score 5-6—Very low food security

For some reporting purposes, the food security status of households with raw score 0-1 is described as food secure and the two categories “low food security” and “very low food security” in combination are referred to as food insecure.

```{r food security, echo= FALSE, results='asis',fig.align='left' }
low_fs <- sum(df$fs == "low")/nrow(df)
low_ns <- sum(df$ns == "low", na.rm = T)/nrow(df)
low_fsns <- {df |> filter(fs == "low" & ns == "low") |> nrow()}/sum(df$fs == "low")

na_table <- df |>  summarise(across(c(q1a, q1b, q3, q4, q5, q6), ~sum(. > 97, na.rm = TRUE), .names = "total_{.col}")) %>%
  pivot_longer(cols = starts_with("total_"), names_to = "column", values_to = "count")


na_table <- df |> 
  summarise(across(c(q1a, q1b, q3, q4, q5, q6, q7), ~sum(. > 97, na.rm = TRUE))) |>
  summarize_all(~sum(.))

print("Total NA or Skipped values for each of the food/nutrition security questions")
kable(na_table)


```
### `r percent(low_fs)` of the AANHPI population face low food security and `r percent(low_ns)` face low nutrition security.
### Of those who face low food security, `r percent(low_fsns)` also face low nutrition security.

## Chi Square evaluation for demographic categories

``` {r chi square, echo = FALSE}

demo_list <- c("asianorigin", "age4", "income4", "region4", "coo")

chisq_fx <- function(demo){

    chisq <- chisq.test(table(df[[demo]], df[["fs"]]))
    sig <- if_else(chisq$p.value <0.05, "a significant", "not a significant")
    print(chisq)
    print(paste("There is", sig, "result between", demo, "and food security"))
}


invisible(lapply(demo_list, chisq_fx))

#library(corrplot)
#round(chisq$residuals, 3)
#corrplot(chisq$residuals, is.cor = FALSE)

```


## Age Breakdown of Food Security 

```{r age, echo=FALSE}
# Age breakdown
age <- df |> group_by(fs, age4) |> 
  summarise(count = n())  |>
  group_by(age4)|>
  mutate(proportional_count = count / sum(count)) |>
  select(-count) |>
  pivot_wider(names_from = age4, values_from = proportional_count, values_fill = 0)

kable(age)

```

## Ethnicity Breakdown of Food Security


``` {r asianorigin, echo = FALSE}
# Asian origin breakdown
ao <- df |> group_by(fs, asianorigin) |> 
  summarise(count = n())|> 
  group_by(asianorigin)|>
  mutate(proportional_count = count / sum(count)) |>
  select(-count) 

kable(ao |>
  pivot_wider(names_from = asianorigin, values_from = proportional_count, values_fill = 0))

ggplot(ao, aes(x=asianorigin, y = proportional_count, fill = fs)) + 
  geom_bar(stat="identity", show.legend=F) + coord_flip() + 
  scale_fill_manual(values = c('#00BFC4', '#F8766D')) + 
  facet_wrap(~fs, scales = "free_y")


svy <- svydesign(ids=~1, weights = ~weight, data = df)


ao_svy <- svyby(~fs, by = ~asianorigin, design = svy, FUN = svymean) |> as_tibble()

kable(ao_svy)

```

## Age Breakdown for Demographic Group

```{r age and demo, echo = FALSE}
demo_fx <- function(demo) {
  df <- df |> filter(asianorigin == demo) |> group_by(fs, age4) |> 
  summarise(count = n())  |>
  group_by(age4)|>
  mutate(proportional_count = count / sum(count)) |>
  select(-count) |>
  pivot_wider(names_from = age4, values_from = proportional_count, values_fill = 0)
  
  kable(df, caption = demo)
}

lapply(unique(df$asianorigin), demo_fx)

```

## Country of Origin Breakdown
```{r coo, echo = FALSE}
# Country of origin breakdown
coo <- df |> group_by(fs, coo) |> 
  summarise(count = n())|> 
  group_by(coo)|>
  mutate(proportional_count = count / sum(count)) |>
  select(-count) |>
  pivot_wider(names_from = coo, values_from = proportional_count, values_fill = 0)
kable(coo)

```

## Nutrition Security
Calculating low nutrition security for those who answered "somewhat hard", "hard", or "very hard" to question 1 in the nutrition screener.

```{r nutrition security, echo = FALSE}

kable(df |> count(ns))
```

## State Breakdown
Calculating low nutrition security for those who answered "somewhat hard", "hard", or "very hard" to question 1 in the nutrition screener.

```{r nutrition security by state, echo = FALSE}
fim_states <- c("AR", "CA", "MA", "NC", "NJ", "NY", "OR", "WA", "DE", "IL", "NM")
fs_states <- df |> filter(state %in% fim_states) |>
  group_by(fs, state) |> 
  summarise(count = n())  |>
  group_by(state)|>
  mutate(proportional_count = count / sum(count)) |>
  select(-count) |>
  pivot_wider(names_from = state, values_from = proportional_count, values_fill = 0)


ns_states <- df |> filter(state %in% fim_states) |>
  group_by(ns, state) |> 
  summarise(count = n())  |>
  group_by(state)|>
  mutate(proportional_count = count / sum(count)) |>
  select(-count) |>
  pivot_wider(names_from = state, values_from = proportional_count, values_fill = 0)


kable(fs_states)
kable(ns_states)

```
