---
title: "Regression Analysis for FS and NS"
author: "Tazz Orchi"
date: "2024-01-24"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_chunk$set(warning = FALSE, message = FALSE) 

setwd("/Users/torchi/Documents/GitHub/norc")

source("001_data_processing.R")
source("002_recode.R")

library(ggplot2)
library(glmnet)
library(stargazer)
library(jtools)
library(tidyverse)
library(janitor)
library(haven)
library(sjPlot)
```

## Comparing Demographics differences across questions concerning FS

```{r fx for y/n, include = FALSE}
likert_fx_y_n <- function(new_col_name, org_col){
  df <- df |> mutate(
    {{new_col_name}} := case_when(
      .data[[org_col]] == 1 ~ 1,
      .data[[org_col]] > 1 ~ 0)
  )
  return(df)
}
```

```{r dichotomize fs questions, include=FALSE}
df <- likert_fx_often("not_last", "q1a")
df <- likert_fx_often("balance", "q1b")
df <- likert_fx_y_n("meal_size", "q3")
df <- likert_fx_often("months", "q4")
df <- likert_fx_y_n("eat_less", "q5")
df <- likert_fx_y_n("hungry", "q6")
```

```{r origin}
#checking sample size per demographic
table(df$asianorigin_l)
```

Individuals who are Vietnamese or NHPI are 2.51 and 3.56 times as likely, respectively to say that it is sometimes/often true that the food they purchased did not last when controlling for income and region.

```{r reference fs q1a}
glm <- glm(not_last ~ relevel(factor(asianorigin_l), ref = 1) + income4_l + region4_l, data = df, family = "binomial")
tab_model(glm)
```

```{r reference fs q1b}
glm <- glm(balance ~ relevel(factor(asianorigin_l), ref = 1) + income4_l + region4_l, data = df, family = "binomial")
tab_model(glm)
```

```{r reference fs q3}
glm <- glm(meal_size ~ relevel(factor(asianorigin_l), ref = 1) + income4_l + region4_l, data = df, family = "binomial")
tab_model(glm)
```

```{r reference fs q4}
glm <- glm(months ~ relevel(factor(asianorigin_l), ref = 1) + income4_l + region4_l, data = df, family = "binomial")
tab_model(glm)
```

```{r reference fs q5}
glm <- glm(eat_less ~ relevel(factor(asianorigin_l), ref = 1) + income4_l + region4_l, data = df, family = "binomial")
tab_model(glm)
```

```{r reference fs q6}
glm <- glm(hungry ~ relevel(factor(asianorigin_l), ref = 1) + income4_l + region4_l, data = df, family = "binomial")
tab_model(glm)
```

## Comparing Demographics differences across questions concerning NS

Signif: asian origin, lang, income, snap

### Univariate analysis for exposure and outcome variables 

Gender does not have a significant relationship 
```{r q7 gender}
glm <- glm(hard_to_get ~ gender_l, data = df, family = "binomial")
tab_model(glm)
```

Snap does have a significant relationship (0.22 odds ratio for those not enrolled)

```{r q7 snap}
glm <- glm(hard_to_get ~ snap, data = df, family = "binomial")
tab_model(glm)
```

Language spoken at home does have a significant relationship (2.95 odds ratio for tagalog and 1.93 odds ratio for other language)
```{r q7 lang}
glm <- glm(hard_to_get ~ lang_athome_l, data = df, family = "binomial")
tab_model(glm)
```

Income is significant (all brackets)

```{r q7 income}
glm <- glm(hard_to_get ~ income4_l, data = df, family = "binomial")
tab_model(glm)
```

Age is not significant 

```{r q7 age}
glm <- glm(hard_to_get ~ age4_l, data = df, family = "binomial")
tab_model(glm)
```

Education is significant

```{r q7 educ}
glm <- glm(hard_to_get ~ educ5, data = df, family = "binomial")
tab_model(glm)
```

Resulting significant variables: educ5, income4, lang_athome, snap

```{r refernce ns q7}
glm <- glm(hard_to_get ~ asianorigin_l + income4_l + lang_athome_l + snap + educ5, data = df, family = "binomial")
tab_model(glm)
```

```{r refernce ns q7 w/o asian origin}
glm <- glm(hard_to_get ~ income4_l + lang_athome_l + snap + educ5, data = df, family = "binomial")
tab_model(glm)
```
----------------------------------------------------------------------------------------------------------
## Food Security significance

Signif: asian origin, income, region, lang, snap

## Comparing Income

We use Income as a Reference category (people making between 60K-100K) and want to compare the odds ratio of the other categories. 

Those with income under 30K are 3 times as likely to have less food security

```{r income reference}
glm <- glm(low_fs ~ relevel(factor(income4_l), ref = 3) + region4_l + asianorigin_l + lang_athome_l + snap, data = df, family = "binomial")
tab_model(glm)
```
## Comparing Age

```{r age reference}
glm <- glm(low_fs ~ relevel(factor(age4_l), ref = 1) + income4_l + region4_l + snap + asianorigin_l + lang_athome_l, data = df, family = "binomial")
tab_model(glm)
```

## Comparing asianorigin

```{r asianorigin reference}
glm <- glm(low_fs ~ relevel(factor(asianorigin_l), ref = 1) + income4_l + region4_l + lang_athome_l + snap, data = df, family = "binomial")
tab_model(glm)
```

```{r asianorigin reference non factored}
glm <- glm(low_fs ~ asianorigin_l + income4_l + region4_l + lang_athome_l + snap, data = df, family = "binomial")
tab_model(glm)
```

## Comparing Gender

```{r gender reference}
glm <- glm(low_fs ~ relevel(factor(gender_l), ref = 1) + income4_l + region4_l, data = df, family = "binomial")
tab_model(glm)
```

## Comparing employment status 

```{r employ reference}
glm <- glm(low_fs ~ relevel(factor(employ), ref = 1) + income4_l + region4_l + asianorigin_l + snap + lang_athome_l, data = df, family = "binomial")
tab_model(glm)
```

## Comparing Internet access 

```{r internet reference}
glm <- glm(low_fs ~ relevel(factor(internet_l), ref = 1) + income4_l + region4_l + asianorigin_l + snap + lang_athome_l, data = df, family = "binomial")
tab_model(glm)
```

## Comparing housing reference 

```{r housing reference}
glm <- glm(low_fs ~ relevel(factor(housing), ref = 1) + income4_l + region4_l + asianorigin_l + snap + lang_athome_l, data = df, family = "binomial")
tab_model(glm)
```
-----------------------------------------------------------------------------------------
## Looking for intersections for example "People falling in x group are more likely to have internet..." 

```{r not last}
#glm <- glm(not_last ~ relevel(factor(internet), ref = 1) + relevel(factor(asianorigin), ref = 1) +  income4 + region4, data = df, family = "binomial")
#tab_model(glm)
```

```{r internet access}
glm <- glm(internet ~ relevel(factor(asianorigin_l), ref = 1) +  income4_l + region4_l, data = df, family = "binomial")
tab_model(glm)
```

-----------------------------------------------------------------------------------------
## Looking for instersections with snap_enrol and snap_elig

Results suggest strong relationship with income (as expected)
```{r reference snap_enrol}
glm <- glm(snap_enrol ~ relevel(factor(asianorigin_l), ref = 1) + income4_l + region4_l, data = df, family = "binomial")
tab_model(glm)
```

```{r reference snap_elig}
glm <- glm(snap_elig ~ relevel(factor(asianorigin_l), ref = 1) + income4_l + region4_l, data = df, family = "binomial")
tab_model(glm)
```

## Snap enrollment and fs/ns

```{r enrol and fs}
glm <- glm(low_fs ~ snap_enrol + relevel(factor(asianorigin_l), ref = 1) + income4_l + region4_l, data = df, family = "binomial")
tab_model(glm)
```

```{r enrol and ns}
glm <- glm(low_ns ~ snap_enrol + relevel(factor(asianorigin_l), ref = 1) + income4_l + region4_l, data = df, family = "binomial")
tab_model(glm)
```

## Snap eligibility and fs/ns

```{r elig and fs}
glm <- glm(low_fs ~ snap_elig + relevel(factor(asianorigin_l), ref = 1) + income4_l + region4_l, data = df, family = "binomial")
tab_model(glm)
```

```{r lig and ns}
glm <- glm(low_ns ~ snap_elig + relevel(factor(asianorigin_l), ref = 1) + income4_l + region4_l, data = df, family = "binomial")
tab_model(glm)
```
