---
title: "regression_dec"
author: "Tazz Orchi"
date: "2024-02-06"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_chunk$set(warning = FALSE, message = FALSE) 

setwd("/Users/torchi/Documents/GitHub/norc")

source("001_data_processing_dec.R")
source("002_recode.R")

library(ggplot2)
library(glmnet)
library(stargazer)
library(jtools)
library(tidyverse)
library(janitor)
library(haven)
library(sjPlot)
```

## Q1A: At home, I tend to eat foods from my culture

Signif: asian origin, age, coo

```{r q1a}
glm <- glm(q1a ~ relevel(factor(asianorigin_l), ref = 1) + coo_l + age4_l, data = df, family = "binomial")
tab_model(glm)
```

## Q1E: Food from my culture are generally healthier than American Food 

Signif: asian origin, age, lang_athome, internet, income 

```{r q1e}
glm <- glm(q1e ~ relevel(factor(asianorigin_l), ref = 1) + lang_athome_l + age4_l + internet_l + income4_l, data = df, family = "binomial")
tab_model(glm)
```
## Q1B I trust my doctor, or other health professionals, for information on healthy eating 

Asian origin is not significant 
Signif: income

```{r q1b}
glm <- glm(q1b ~ income4_l, data = df, family = "binomial")
tab_model(glm)
```

## Q1C: When I am feeling ill, I will eat specific food ingredients to get healthy 

Asian origin is not significant 
Signif: lang, coo

```{r q1c}
glm <- glm(q1c ~ lang_athome_l + coo_l, data = df, family = "binomial")
tab_model(glm)
```

## Q6: I believe food is healing/food for my body 

Asian origin is not significant
Signif: internet, lang

```{r q6}
glm <- glm(q6 ~ lang_athome_l + internet_l, data = df, family = "binomial")
tab_model(glm)
```

## Q7A: Providing more nutrition counseling to patients 

Asian origin is not significant 
Signif: income, internet, age 

```{r q7a}
glm <- glm(q7a ~ income4_l + internet_l + age4_l, data = df, family = "binomial")
tab_model(glm)
```

## Q7B: Teaching patients to cook

No demographic of interest is significant 

## Q7C: Helping pay for healthier food in grocery stores, supermarkets, and/or farmers markets for patients with appropriate medical conditions 

Asian origin is not significant 
Signif: income, lang, age 

```{r q7c}
glm <- glm(q7c ~ lang_athome_l + income4_l + age4_l, data = df, family = "binomial")
tab_model(glm)
```

## Q7D: Havining on-site food grocery or pantry pick-up locations for healthier food for patients with appropriate medical conditions 

Asian origin is not significant 
Signif: coo, age 

```{r q7d}
glm <- glm(q7d ~ coo_l + age4_l, data = df, family = "binomial")
tab_model(glm)
```

## Q7E: Helping to pay for delivery of healthy groceries or meals to homes of patients with appropriate medical conditions 

Signif: asian origin, income, coo, age

```{r q7e}
glm <- glm(q7e ~ relevel(factor(asianorigin_l), ref = 1) + coo_l + age4_l + income4_l, data = df, family = "binomial")
tab_model(glm)
```

## Q8A: I have heard of Medically tailored meals 

Asian origin is not significant 
Signif: coo 

```{r q8a}
glm <- glm(q8a ~ coo_l, data = df, family = "binomial")
tab_model(glm)
```

## Q8B: I have heard of Medically tailored groceries 

No demographic group of interest is significant 

## Q8C: I have heard of Produce prescription programs 

Asian origin is not significant 
Signif: income

```{r q8c}
glm <- glm(q8c ~ income4_l, data = df, family = "binomial")
tab_model(glm)
```

## Q9A: If offered to me, I would participate in regular nutrition counseling and/or cooking education around eating a healthy diet 

No demographic group of interest is significant 

## Q9B: If offered to me, I would participate in Medically tailored meals 

No demographic group of interest is significant 

## Q9C: If offered to me, I would particpate in Medically tailored groceries 

Asian origin is not significant 
Signif: lang 

```{r q9c}
glm <- glm(q9c ~ lang_athome_l, data = df, family = "binomial")
tab_model(glm)
```

## Q9D: If offered to me, I would participate in Produce prescription programs 

Asian origin is not significant 
Signif: income

```{r q9d}
glm <- glm(q9d ~ income4_l, data = df, family = "binomial")
tab_model(glm)
```
