---
title: "regression"
author: "Tazz Orchi"
date: "2024-01-24"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_chunk$set(warning = FALSE, message = FALSE) 

setwd("/Users/torchi/Documents/GitHub/norc")

source("001_data_processing.R")
source("002_recode.R")

library(ggplot2)
library(glmnet)
library(stargazer)
```
Linear Regression

Age as continuous variable (probably better to do logistic or non-linear regression)

```{r linear, results='asis'}
lm1 <- lm(low_fs ~ age + income, data = df)
stargazer(lm1, type = "text", title = "Linear Regression Summary")

ggplot(df, aes(x = low_fs, y = age)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE, color = "blue") +
  labs(title = "Linear Regression", x = "Independent Variable", y = "Dependent Variable")
```

Conclusion: The low R-squared and adjusted R-squared suggests that this model does not explain the population very well.
#Standard error is high and with an F-stat close to 1 we can conclude that this model is not very statistically significant overall

Logistic Regression 

Age vs low_fs 

```{r logit1, results='asis'}
logit_model1 <- glm(low_fs ~ age + income4, data = df, family = "binomial")
stargazer(logit_model1, type = "text", title = "Logistic Regression Summary")

ggplot(df, aes(x = age, y = low_fs)) +
  geom_point() +
  stat_smooth(method = "glm", family = "binomial", se = FALSE, color = "blue") +
  labs(title = "Logistic Regression", x = "Independent Variable", y = "Binary Dependent Variable")
```

Use Income as a Reference category (people above 100K+ ), odds ratio for other income categories 


lm5 <- lm(length_of_stay ~ relevel(factor(type_of_patient), ref = 2) + age , data = treatment5)

Conclusion: Very slight negative relationship as age increases, but not statistically significant. For every one unit increase in age, there is .02% decrease in low_fs

Log likelihood indicates this model fits the dataset well, may be overfitting

Using low_fs we can compare how much of a correlation there is with other listed in the questionnaire. Opting to control for age and income. 

q8a:Healthy foods are too expensive (often/sometimes true, never true, etc.)

```{r logit2, results='asis'}
logit_model2 <- glm(low_fs ~ q8a + age + income, data = df, family = "binomial")
stargazer(logit_model2, type = "text", title = "Logistic Regression Summary")
```

q1b:We couldn't afford to eat balanced meals (often/sometimes true, never true, etc.)

Shows significant negative relationship between responses for q1b (I believe responses associated with a higher number) and low_fs

What is the cut off for Sample-size* --> Based on distribution of data. 

```{r logit3, results='asis'}
logit_model3 <- glm(low_fs ~ q1b + age + income, data = df, family = "binomial")
stargazer(logit_model3, type = "text", title = "Logistic Regression Summary")
```

q5: In the last 12 months, did you ever eat less than you felt you should because there wasn't enough money for food?
Significant negative correlation for q5 and income 

```{r logit4, results='asis'}
logit_model4 <- glm(low_fs ~ q5 + age + income, data = df, family = "binomial")
stargazer(logit_model4, type = "text", title = "Logistic Regression Summary")
```

