---
title: "Regression Analysis for FS and NS"
author: "Tazz Orchi"
date: "2024-01-24"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_chunk$set(warning = FALSE, message = FALSE) 

setwd("/Users/torchi/Documents/GitHub/norc")

source("001_data_processing.R")
source("002_recode.R")

library(ggplot2)
library(glmnet)
library(stargazer)
library(jtools)
```

## Comparing Income

We use Income as a Reference category (people making between 60K-100K) and want to compare the odds ratio of the other categories. 

Those with income under 30K are 3 times as likely to have less food security

```{r income reference}
glm <- glm(low_fs ~ relevel(factor(income4), ref = 3) + hhsize, data = df, family = "binomial")
#stargazer(glm, type = "text", title = "Income Reference")
summ(glm, confint = TRUE, digits = 3, exp = TRUE)
```
## Comparing Age

```{r age reference}
glm <- glm(low_fs ~ relevel(factor(age4), ref = 1) + income4 + hhsize, data = df, family = "binomial")
#stargazer(glm, type = "text", title = "Income Reference")
summ(glm, confint = TRUE, digits = 3, exp = TRUE)
```

## Comparing asianorigin

```{r asianorigin reference}
glm <- glm(low_fs ~ relevel(factor(asianorigin), ref = 1) + income4 + hhsize, data = df, family = "binomial")
#stargazer(glm, type = "text", title = "Income Reference")
summ(glm, confint = TRUE, digits = 3, exp = TRUE)
```

```{r asianorigin reference}
glm <- glm(low_fs ~ asianorigin + income4 + hhsize, data = df, family = "binomial")
#stargazer(glm, type = "text", title = "Income Reference")
summ(glm, confint = TRUE, digits = 3, exp = TRUE)
```

## Comparing Gender

```{r gender reference}
glm <- glm(low_fs ~ relevel(factor(gender), ref = 1) + income4 + hhsize, data = df, family = "binomial")
#stargazer(glm, type = "text", title = "Income Reference")
summ(glm, confint = TRUE, digits = 3, exp = TRUE)
```

## Comparing employment status 

```{r employ reference}
glm <- glm(low_fs ~ relevel(factor(employ), ref = 1) + income4 + hhsize, data = df, family = "binomial")
#stargazer(glm, type = "text", title = "Income Reference")
summ(glm, confint = TRUE, digits = 3, exp = TRUE)
```

## Comparing Internet access 

```{r internet reference}
glm <- glm(low_fs ~ relevel(factor(internet), ref = 1) + income4 + hhsize, data = df, family = "binomial")
#stargazer(glm, type = "text", title = "Income Reference")
summ(glm, confint = TRUE, digits = 3, exp = TRUE)
```

## Comparing housing reference 

```{r housing reference}
glm <- glm(low_fs ~ relevel(factor(housing), ref = 1) + income4 + hhsize, data = df, family = "binomial")
#stargazer(glm, type = "text", title = "Income Reference")
summ(glm, confint = TRUE, digits = 3, exp = TRUE)
```
_______________________________________________________________________________

## Regression Analysis for low_fs

### Q8A

#### Healthy foods are too expensive (often/sometimes true, never true, etc.)

```{r logit1, results='asis'}
logit_model1 <- glm(low_fs ~ q8a + age + income4, data = df, family = "binomial")
#stargazer(logit_model1, type = "text", title = "Logistic Regression Summary")

#ggplot(df2, aes(x = age, y = low_fs)) +
  #geom_point() +
  #stat_smooth(method = "glm", family = "binomial", se = FALSE, color = "blue") +
  #labs(title = "Logistic Regression", x = "Independent Variable", y = "Binary Dependent Variable")

summ(logit_model1, confint = TRUE, digits = 3, exp = TRUE)
```

#### Conclusion:  

### Q8B 

#### There aren't a lot of healthy food choices at the stores where I usually shop 

```{r logit2, results='asis'}
logit_model2 <- glm(low_fs ~ q8b + age + income, data = df, family = "binomial")
#stargazer(logit_model2, type = "text", title = "Logistic Regression Summary")

summ(logit_model2, confint = TRUE, digits = 3, exp = TRUE)
```

#### Conclusion: 

### Q8C

#### Stores or food pantries with healthy foods are too far away or hard to reach 

```{r logit3, results='asis'}
logit_model3 <- glm(low_fs ~ q8c + age + income, data = df, family = "binomial")
#stargazer(logit_model3, type = "text", title = "Logistic Regression Summary")

summ(logit_model3, confint = TRUE, digits = 3, exp = TRUE)
```
#### Conclusion:

### Q8d

#### I don't have a car or other transportation to reach stores or food pantries that have healthy foods 

```{r logit4, results='asis'}
logit_model4 <- glm(low_fs ~ q8d + age + income, data = df, family = "binomial")
#stargazer(logit_model3, type = "text", title = "Logistic Regression Summary")

summ(logit_model4, confint = TRUE, digits = 3, exp = TRUE)
```
#### Conclusion 

### Q8e

#### I don't have enough time to shope for healthy foods 

```{r logit5, results='asis'}
logit_model5 <- glm(low_fs ~ q8e + age + income, data = df, family = "binomial")
#stargazer(logit_model3, type = "text", title = "Logistic Regression Summary")

summ(logit_model5, confint = TRUE, digits = 3, exp = TRUE)
```
#### Conclusion 

### Q8f

#### I don't have enough time to cook healthy foods

```{r logit6, results='asis'}
logit_model6 <- glm(low_fs ~ q8f + age + income, data = df, family = "binomial")
#stargazer(logit_model3, type = "text", title = "Logistic Regression Summary")

summ(logit_model6, confint = TRUE, digits = 3, exp = TRUE)
```
#### Conclusion

### Q8g

#### My cooking equipment or storage space is not enough to prepapre healthy foods 

```{r logit7, results='asis'}
logit_model7 <- glm(low_fs ~ q8g + age + income, data = df, family = "binomial")
#stargazer(logit_model3, type = "text", title = "Logistic Regression Summary")

summ(logit_model7, confint = TRUE, digits = 3, exp = TRUE)
```

#### Conclusion:

### Q8h

#### Question content

```{r logit8, results='asis'}
logit_model8 <- glm(low_fs ~ q8h + age + income, data = df, family = "binomial")
#stargazer(logit_model3, type = "text", title = "Logistic Regression Summary")

summ(logit_model8, confint = TRUE, digits = 3, exp = TRUE)
```

#### Conclusion: 

### Q8i

#### Question Content

```{r logit9, results='asis'}
logit_model9 <- glm(low_fs ~ q8i + age + income, data = df, family = "binomial")
#stargazer(logit_model3, type = "text", title = "Logistic Regression Summary")

summ(logit_model9, confint = TRUE, digits = 3, exp = TRUE)
```

#### Conclusion

### Q8j

#### Question Content

```{r logit10, results='asis'}
logit_model10 <- glm(low_fs ~ q8j + age + income, data = df, family = "binomial")
#stargazer(logit_model3, type = "text", title = "Logistic Regression Summary")

summ(logit_model10, confint = TRUE, digits = 3, exp = TRUE)
```

#### Conclusion 

### Q8k

#### Question Content

```{r logit11, results='asis'}
logit_model11 <- glm(low_fs ~ q8k + age + income, data = df, family = "binomial")
#stargazer(logit_model3, type = "text", title = "Logistic Regression Summary")

summ(logit_model11, confint = TRUE, digits = 3, exp = TRUE)
```

#### Conclusion 

### Q8l

#### Question Content

```{r logit12, results='asis'}
logit_model12 <- glm(low_fs ~ q8l + age + income, data = df, family = "binomial")
#stargazer(logit_model3, type = "text", title = "Logistic Regression Summary")

summ(logit_model12, confint = TRUE, digits = 3, exp = TRUE)
```
#### Conclusion 

### Q8m

#### Question Content

```{r logit13, results='asis'}
logit_model13 <- glm(low_fs ~ q8m + age + income, data = df, family = "binomial")
#stargazer(logit_model3, type = "text", title = "Logistic Regression Summary")

summ(logit_model13, confint = TRUE, digits = 3, exp = TRUE)
``` 

#### Conclusion 

### Q9

#### Question Content

```{r logit14, results='asis'}
logit_model14 <- glm(low_fs ~ q9 + age + income, data = df, family = "binomial")
#stargazer(logit_model3, type = "text", title = "Logistic Regression Summary")

summ(logit_model14, confint = TRUE, digits = 3, exp = TRUE)
``` 

#### Conclusion

### Q10

#### Question Content

```{r logit15, results='asis'}
logit_model15 <- glm(low_fs ~ q10 + age + income, data = df, family = "binomial")
#stargazer(logit_model3, type = "text", title = "Logistic Regression Summary")

summ(logit_model15, confint = TRUE, digits = 3, exp = TRUE)
``` 

#### Conclusion

## Regression Analysis for low_ns

### Q8A

#### Healthy foods are too expensive (often/sometimes true, never true, etc.)

```{r logit16, results='asis'}
logit_model16 <- glm(low_ns ~ q8a + age + income4, data = df, family = "binomial")
#stargazer(logit_model1, type = "text", title = "Logistic Regression Summary")

#ggplot(df2, aes(x = age, y = low_fs)) +
  #geom_point() +
  #stat_smooth(method = "glm", family = "binomial", se = FALSE, color = "blue") +
  #labs(title = "Logistic Regression", x = "Independent Variable", y = "Binary Dependent Variable")

summ(logit_model16, confint = TRUE, digits = 3, exp = TRUE)
```

#### Conclusion:  

### Q8B 

#### There aren't a lot of healthy food choices at the stores where I usually shop 

```{r logit2, results='asis'}
logit_model2 <- glm(low_ns ~ q8b + age + income, data = df, family = "binomial")
#stargazer(logit_model2, type = "text", title = "Logistic Regression Summary")

summ(logit_model2, confint = TRUE, digits = 3, exp = TRUE)
```

#### Conclusion: 

### Q8C

#### Stores or food pantries with healthy foods are too far away or hard to reach 

```{r logit3, results='asis'}
logit_model3 <- glm(low_ns ~ q8c + age + income, data = df, family = "binomial")
#stargazer(logit_model3, type = "text", title = "Logistic Regression Summary")

summ(logit_model3, confint = TRUE, digits = 3, exp = TRUE)
```
#### Conclusion:

### Q8d

#### I don't have a car or other transportation to reach stores or food pantries that have healthy foods 

```{r logit3, results='asis'}
logit_model4 <- glm(low_ns ~ q8d + age + income, data = df, family = "binomial")
#stargazer(logit_model3, type = "text", title = "Logistic Regression Summary")

summ(logit_model4, confint = TRUE, digits = 3, exp = TRUE)
```
#### Conclusion 

### Q8e

#### I don't have enough time to shope for healthy foods 

```{r logit3, results='asis'}
logit_model5 <- glm(low_ns ~ q8e + age + income, data = df, family = "binomial")
#stargazer(logit_model3, type = "text", title = "Logistic Regression Summary")

summ(logit_model5, confint = TRUE, digits = 3, exp = TRUE)
```
#### Conclusion 

### Q8f

#### I don't have enough time to cook healthy foods

```{r logit3, results='asis'}
logit_model6 <- glm(low_ns ~ q8f + age + income, data = df, family = "binomial")
#stargazer(logit_model3, type = "text", title = "Logistic Regression Summary")

summ(logit_model6, confint = TRUE, digits = 3, exp = TRUE)
```
#### Conclusion

### Q8g

#### My cooking equipment or storage space is not enough to prepapre healthy foods 

```{r logit3, results='asis'}
logit_model7 <- glm(low_ns ~ q8g + age + income, data = df, family = "binomial")
#stargazer(logit_model3, type = "text", title = "Logistic Regression Summary")

summ(logit_model7, confint = TRUE, digits = 3, exp = TRUE)
```

#### Conclusion:

### Q8h

#### Question content

```{r logit3, results='asis'}
logit_model8 <- glm(low_ns ~ q8h + age + income, data = df, family = "binomial")
#stargazer(logit_model3, type = "text", title = "Logistic Regression Summary")

summ(logit_model8, confint = TRUE, digits = 3, exp = TRUE)
```

#### Conclusion: 

### Q8i

#### Question Content

```{r logit3, results='asis'}
logit_model9 <- glm(low_ns ~ q8i + age + income, data = df, family = "binomial")
#stargazer(logit_model3, type = "text", title = "Logistic Regression Summary")

summ(logit_model9, confint = TRUE, digits = 3, exp = TRUE)
```

#### Conclusion

### Q8j

#### Question Content

```{r logit3, results='asis'}
logit_model10 <- glm(low_ns ~ q8j + age + income, data = df, family = "binomial")
#stargazer(logit_model3, type = "text", title = "Logistic Regression Summary")

summ(logit_model10, confint = TRUE, digits = 3, exp = TRUE)
```

#### Conclusion 

### Q8k

#### Question Content

```{r logit3, results='asis'}
logit_model11 <- glm(low_ns ~ q8k + age + income, data = df, family = "binomial")
#stargazer(logit_model3, type = "text", title = "Logistic Regression Summary")

summ(logit_model11, confint = TRUE, digits = 3, exp = TRUE)
```

#### Conclusion 

### Q8l

#### Question Content

```{r logit3, results='asis'}
logit_model12 <- glm(low_ns ~ q8l + age + income, data = df, family = "binomial")
#stargazer(logit_model3, type = "text", title = "Logistic Regression Summary")

summ(logit_model12, confint = TRUE, digits = 3, exp = TRUE)
```
#### Conclusion 

### Q8m

#### Question Content

```{r logit3, results='asis'}
logit_model13 <- glm(low_ns ~ q8m + age + income, data = df, family = "binomial")
#stargazer(logit_model3, type = "text", title = "Logistic Regression Summary")

summ(logit_model13, confint = TRUE, digits = 3, exp = TRUE)
``` 

#### Conclusion 

